An Embedding Framework for Consistent Polyhedral Surrogates

### 2022-03-01 poly-embed-journal/poly-embed-journal.tex
Pre meeting review

When using our framework to study an existing surrogate $L:\reals^d \to \reals^\Y_+$, often the first step is determining the loss it embeds.
To this end, we suggest the following general approach.
First, for each $y\in\Y$, divide $\reals^d$ into a finite number of polyhedral regions on which $L(\cdot)_y$ is an affine function (\S~\ref{sec:lovasz-hinge}, \ref{sec:top-k}).
Often these regions are straightforward to identify based on the form of $L$.\jessie{tbh this sentence feels like a lie lol}
Letting $\Sc\subset\reals^d$ be the union of vertices of these polyhedral regions, conclude that $\Sc$ is a finite representative set for $L$~\citep[Statement 3.1.7]{grunbaum2013convex}.
By Proposition~\ref{prop:representative-embeds-restriction}, $L$ embeds $L|_\Sc$.
From here one can further remove redundant reports until one arrives at a tight embedding if desired.
Once the embedded discrete loss is known, the behavior of the surrogate becomes more clear: what problem it is solving, and for which restrictions on conditional label distributions is it consistent for the original problem (\S~\ref{sec:winge}, \ref{sec:top-k}).
Moreover, while embedding guarantees the existence of a calibrated link function, Construction~\ref{const:eps-thick-link} provides a framework to both verify proposed link functions and construct new ones.
A key step in Construction~\ref{const:eps-thick-link} is constructing the link candidate function $\Psi$, which yields the possible values any $\epsilon$-separated link $\psi$ could map to; this in turn provides a handy tool to verify the calibration of a proposed link (\S~\ref{sec:abstain}, \ref{sec:top-k}).
\raft{We should discuss this a bit in the examples where appropriate, e.g. WW, and then forward ref in parens here to the relevant subsection(s)}

For many target problems, the search for calibrated surrogates has been restricted to those accommodating a particular link function, such as $k$ largest coordinates of the surrogate report for the top-$k$ problem (\S~\ref{sec:top-k}).
In these cases, as we observe in \S~\ref{sec:calibration}, our link construction can also be used to verify the calibration of a given proposed link.
More generally, however, our results suggest that researchers could explore surrogates beyond the link function they had in mind (\S~\ref{sec:lovasz-hinge}).
In particular, one can instead search for surrogates that embed the correct discrete loss, and use Construction~\ref{const:eps-thick-link} to construct the link.

@@

\citet*{wang2020weston} use the embedding framework to construct and prove the calibration of the Weston-Watkins surrogate for the \emph{ordered partition} loss, and in turn, recover the result of inconsistency with respect to 0-1 loss.
%An ordered partition on $[n] := \{1, \ldots, n\}$ can be defined by a nested sequence of tuples
%Let $T = \{T_1, \ldots, T_k\}$
The report space for this discrete loss can be defined in terms of nested subsets of $[n] := \{1, \ldots, n\}$, as follows.%
\footnote{To recover the partition of~\citet{wang2020weston}, one can define $S_i = T_i \setminus T_{i-1}$.}
\begin{align*}
\T = \{ (T_0,\ldots,T_k) \mid k \geq 2, \emptyset = T_0 \subsetneq T_1 \subsetneq \ldots \subsetneq T_k = [n]\}~.
\end{align*}
The ordered partition target loss $\ell^{\OP} : \T \to \reals^\Y_+$ is then defined by
\begin{align*}
\ell^\OP(T)_y &= \sum_{i=1}^{k} \left(|T_{i}| \cdot \Ind{y \not \in T_{i-1}} \right) -1~.~
\end{align*}
%\raf{Jessie, could you check that the newer form is correct?  I messed with a couple things, and decided not to clutter the tex with the old stuff -- maybe check the diff if it would help, or go straight to the original version.}\jessie{Confirmed}

The ordered partition loss can be interpreted as a variation of 0-1 loss where one reports a nested sequence of sets, and the punishment for the outcome $y$ is the cardinality of the first set containing $y$, plus the cardinality of all earlier sets.
\citet{wang2020weston} show that $L_{WW}$ embeds $\ell^\OP$, with the embedding
$\varphi : \T \to \reals^n$ given by $\varphi(T)_j = -(i-1)$ for all $j \in T_i \setminus T_{i-1}$.
They then apply Theorem~\ref{thm:link-main} to conclude that there exists a link function $\psi$ such that $(L_{WW},\psi)$ is calibrated with respect to $\ell^\OP$; however, they do not construct the link.
\jessie{Natural link to test is a rounding link, yeah?}
\raf{Jessie, could you add something here about the figure and dotted lines, which show conditions under which WW is consistent for 0-1?}

>>>>

When using our framework to study an existing surrogate $L:\reals^d \to \reals^\Y_+$, often the first step is determining the loss it embeds.
To this end, we suggest the following general approach.
First, for each $y\in\Y$, divide $\reals^d$ into a finite number of polyhedral regions on which $L(\cdot)_y$ is an affine function (\S~\ref{sec:lovasz-hinge}, \ref{sec:top-k}).
Often these regions are straightforward to identify based on the form of $L$.\jessie{tbh this sentence feels like a lie lol}
Letting $\Sc\subset\reals^d$ be the union of vertices of these polyhedral regions, conclude that $\Sc$ is a finite representative set for $L$~\citep[Statement 3.1.7]{grunbaum2013convex}.
By Proposition~\ref{prop:representative-embeds-restriction}, $L$ embeds $L|_\Sc$.
From here one can further remove redundant reports until one arrives at a tight embedding if desired.
Once the embedded discrete loss is known, the behavior of the surrogate becomes more clear: what problem it is solving, and for which restrictions on conditional label distributions is it consistent for the original problem (\S~\ref{sec:winge}, \ref{sec:top-k}).
Moreover, while embedding guarantees the existence of a calibrated link function, Construction~\ref{const:eps-thick-link} provides a framework to both verify proposed link functions and construct new ones.
A key step in Construction~\ref{const:eps-thick-link} is constructing the link candidate function $\Psi$, which yields the possible values any $\epsilon$-separated link $\psi$ could map to; this in turn provides a tool to verify the calibration of a proposed link (\S~\ref{sec:abstain}, \ref{sec:top-k}).
\raft{We should discuss this a bit in the examples where appropriate, e.g. WW, and then forward ref in parens here to the relevant subsection(s)}

\jessiet{Commented out paragraph below; feels redundant now. - Mar 1, 22}
%For many target problems, the search for calibrated surrogates has been restricted to those accommodating a particular link function, such as $k$ largest coordinates of the surrogate report for the top-$k$ problem (\S~\ref{sec:top-k}).
%In these cases, as we observe in \S~\ref{sec:calibration}, our link construction can also be used to verify the calibration of a given proposed link.
%More generally, however, our results suggest that researchers could explore surrogates beyond the link function they had in mind (\S~\ref{sec:lovasz-hinge}).
%In particular, one can instead search for surrogates that embed the correct discrete loss, and use Construction~\ref{const:eps-thick-link} to construct the link.

@@

\citet*{wang2020weston} use the embedding framework to construct and prove the calibration of the Weston-Watkins surrogate for the \emph{ordered partition} loss, and in turn, recover the result of inconsistency with respect to 0-1 loss.
%An ordered partition on $[n] := \{1, \ldots, n\}$ can be defined by a nested sequence of tuples
%Let $T = \{T_1, \ldots, T_k\}$
The report space for this discrete loss can be defined in terms of nested subsets of $[n] := \{1, \ldots, n\}$, as follows.%
\footnote{To recover the partition of~\citet{wang2020weston}, one can define $S_i = T_i \setminus T_{i-1}$.}
\begin{align*}
\T = \{ (T_0,\ldots,T_k) \mid k \geq 1, \emptyset = T_0 \subsetneq T_1 \subsetneq \ldots \subsetneq T_k = [n]\}~.
\end{align*}

The ordered partition target loss $\ell^{\OP} : \T \to \reals^\Y_+$ is then defined by
\begin{align*}
\ell^\OP(T)_y &= \sum_{i=1}^{k} \left(|T_{i}| \cdot \Ind{y \not \in T_{i-1}} \right) -1~.~
\end{align*}
%\raf{Jessie, could you check that the newer form is correct?  I messed with a couple things, and decided not to clutter the tex with the old stuff -- maybe check the diff if it would help, or go straight to the original version.}\jessie{Confirmed}

The ordered partition loss can be interpreted as a variation of 0-1 loss where one reports a nested sequence of sets, and the punishment for the outcome $y$ is the cardinality of the first set containing $y$, plus the cardinality of all earlier sets.
\citet{wang2020weston} show that $L_{WW}$ embeds $\ell^\OP$, with the embedding
$\varphi : \T \to \reals^n$ given by $\varphi(T)_j = -(i-1)$ for all $j \in T_i \setminus T_{i-1}$.
\citeauthor{wang2020weston} then apply Theorem~\ref{thm:link-main} to conclude that there exists a link function $\psi$ such that $(L_{WW},\psi)$ is calibrated with respect to $\ell^\OP$; however, they do not construct the link.
\jessie{Natural link to test is a rounding link, yeah?}
\raf{Jessie, could you add something here about the figure and dotted lines, which show conditions under which WW is consistent for 0-1?}
